Summary of the things that I learned

### 2024-11-26 200-category-theory.tex
Minor improvements

\begin{remark}
  In classical mathematics, the only structure of a category is that of the objects and morphisms. Therefore, the properties in Remark \ref{rem:classical-karoubi-universal} characterize a classical category uniquely up to adjoint equivalence. However, in univalent foundations, categories have additional structure, which is given by identities between objects. Therefore, there can be structurally different categories which satisfy this universal property and we need an additional constraint to single out the `right' one. However, there are actually two branches of category theory in univalent foundations, each giving its own constraint.

@@

Note that there are two different ways to translate the definition at the end of Remark \ref{rem:classical-karoubi-universal} to univalent foundations. We can either interpret the existence of the object $ X $ and the retraction $ (r, s) : F \triangleleft \yo(X) $ as additional \textit{structure} on $ F $, or we can treat it as a \textit{property} and ask for \textit{mere existence} (see Definition \ref{def:mere-existence}) of $ X $, $ r $ and $ s $. This gives rise to two different categories:

>>>>

\begin{remark}
  In classical mathematics, the only structure of a category is that of the objects and morphisms. Therefore, the properties in Remark \ref{rem:classical-karoubi-universal} characterize a classical category uniquely up to adjoint equivalence. However, in univalent foundations, categories have additional structure in the form of the identity types between objects. Therefore, there can be structurally different categories which satisfy this universal property and we need an additional constraint to single out the `right' one. In fact, there are two branches of category theory in univalent foundations, each giving its own constraint.

@@

There are two different ways to translate the definition at the end of Remark \ref{rem:classical-karoubi-universal} to univalent foundations. We can either interpret the existence of the object $ X $ and the retraction $ (r, s) : F \triangleleft \yo(X) $ as additional \textit{structure} on $ F $, or we can treat it as a \textit{property} and ask for \textit{mere existence} (see Definition \ref{def:mere-existence}) of $ X $, $ r $ and $ s $. This gives rise to two different categories:
